\documentclass[11pt, a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage{xcolor}
    \usepackage{fontawesome}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=20in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%


    \begin{document}
\vspace*{-20pt}

    

%==== Profile ====%

\begin{center}
	{\Huge {\textbf{Adithya Balaji}}}\\
	Ulm, Germany $\cdot$ adithya.b94@gmail.com $\cdot$ (+49) 15510 782415\\
\end{center}

\vspace{5mm}

\header {\textbf{PROFILE}}
\vspace{1mm}
Experienced software engineer with international exposure and commitment to detail oriented, accurate work and background in diverse areas such as Artificial Intelligence, Computer vision, Data Engineering, Robotics and DevOps 

\vspace{5mm}

%==== Experience ====%
\header{\textbf{PROFESSIONAL EXPERIENCE}}
\vspace{1mm}

\textbf{Embedded AI Developer} \hfill Ulm, Germany\\

\textbf{Huber Automotive AG} \hfill Dec 2022 - Present\\
\begin{itemize} \itemsep 1pt
        \item Developed edge AI models optimized for microcontrollers and processors, using frameworks such as TensorFlow Lite, PyTorch, and Explainable AI (XAI) techniques to improve transparency and accountability of models.
        \item Utilized computer vision techniques, including object detection and tracking, to enable intelligent perception in robotics and edge AI applications.
        \item Conducted sensor calibration and simulation to enable accurate and reliable perception in robotics and edge AI applications.
        \item Integrated with the Robot Operating System (ROS) to enable efficient development and deployment of robotics and edge AI applications.
        \item Possess experience with Adaptive Autosar, ASPICE, and ISO 26262, enabling development of safety-critical systems for automotive and other industries.
\end{itemize}

\textbf{AI Research Intern } \hfill Nantes, France\\

\textbf{Reliev} \hfill Dec 2021 - September 2022\\
\begin{itemize} \itemsep 1pt
        \item Conducted extensive research on Epilepsy detection for bibliography purposes.
        \item Utilized real-time time-series databases for signal processing and developed machine learning models to detect seizures in epileptic patients.
        \item Extensive experience with feature engineering and selection techniques.
        \item Designed unsupervised learning models and neural networks to create noise and seizure prediction algorithms.
        \item Performed Unit tests and built CI/CD pipelines to ensure the quality and efficiency of codebase.
        \item Skilled in Git, DevOps, Docker, and Linux-based development.
        \item Built interactive visualizations and dashboards using Plotly and Dash to display and interpret results.
\end{itemize}

\textbf{Data and Automation Engineer} \hfill Chennai, India\\

\textbf{EMIS Health} \hfill Dec 2017 - Dec 2019\\
\begin{itemize} \itemsep 1pt
        \item Developed Machine Learning models to analyze speech input of emergency calls for NHS, United Kingdom.
        \item Worked on multiple Data Science and Analytics projects and integrated them with Datalake, delivering actionable insights to customers.
        \item Extensive experience with Big Data technologies such as Apache Spark, Kafka, and Airflow, including testing data ingestion processes.
        \item Proficient in working with both SQL and NoSQL databases, including SQL Server, Postgres, Presto, and DynamoDB.
        \item Developed and implemented QA automation tests utilizing FlaUI, xUnit, Specflow, and Cucumber with C\# for .NET applications.
        \item Skilled in working with various tools and platforms including AWS, Docker, Azure DevOps, CI/CD, Atlassian, and JIRA X-Ray
        \end{itemize}

\textbf{Associate Software Engineer} \hfill Chennai, India\\

\textbf{Accenture} \hfill Dec 2016 - Dec 2017\\
\begin{itemize} \itemsep 1pt
        \item Conducted analysis of large-scale telecommunications data utilizing Data Warehousing and ETL techniques.
        \item Created automation frameworks using Python and Selenium to increase testing efficiency and accuracy.
        \item Experience with various tools such as Splunk, Tableau, etc., for data visualization and analysis purposes.
        \item Utilized HP ALM for project management purposes, ensuring that projects were completed on time and within budget.
\end{itemize}

\vspace{2mm}

%==== Education ====%
\header{\textbf{EDUCATION}}
\vspace{3mm}
\textbf{Ecole centrale de Nantes, France}\hfill Jan 2020 - Sept 2022\\
M.Sc Advanced Robotics and AI \hfill \\
\vspace{3mm}
\textbf{Anna University, India}\hfill Aug 2012 - Apr 2016\\
Bachelor of Engineering - Automobile Engineering \hfill \\

\vspace{5mm}
\renewcommand{\arraystretch}{1.5}
%==== TECHNICAL SUMMARY ====%

\header{\textbf{TECHNICAL SUMMARY}}
\vspace{3mm}

\begin{tabular}{ p{5cm}p{5cm} }
Python and AI   &\faCircle \faCircle \faCircle \faCircle \faCircle   \\
Artificial Intelligence   &\faCircle \faCircle \faCircle \faCircle \faCircle \\
Data engineering  &\faCircle \faCircle \faCircle \faCircle \faCircleO  \\
CI/CD and DevOps  &\faCircle \faCircle \faCircle \faCircle \faCircleO \\
Computer vision, ROS, Linux  &\faCircle \faCircle \faCircle \faCircleO \faCircleO  \\
C++, C\#  &\faCircle \faCircle \faCircle \faCircleO \faCircleO  \\
\end{tabular}

\vspace{5mm}
% %==== LANGUAGES ====%
% \header{\textbf{CERTIFICATIONS/ WORKSHOPS / EXTRAS}}
% \vspace{1mm}
% \renewcommand{\arraystretch}{1.5}
% \begin{tabular}{ p{8cm}p{5cm} }
% Foundation Masters in Control and Robotics   &Centrale Nantes  \\
% Machine learning scientist with python    &DataCamp \\
% Data Scientist Nanodegree &Udacity \\
% AI winter school 2021 &MIAI Grenoble and PRAIRIE \\
% \end{tabular}

% \vspace{5mm}

% \newpage

%==== LANGUAGES ====%
\header{\textbf{LANGUAGES}}
\vspace{1mm}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{ p{3cm}p{3cm} }
English   &Bilingual  \\
French   &Intermediate \\
German &Elementary \\
Tamil &Bilingual \\
\end{tabular}

% \vspace{5mm}
% %==== References ====%

% \header{\textbf{REFRENCES}}
% \vspace{3mm}
% \textbf{Prof. Olivier Kermorgant}\hfill Associate Professor of Robotics at Centrale Nantes\\
% olivier.kermorgant@ec-nantes.fr   \hfill +33 (0)2 40 37 69 99\\
% \vspace{3mm}
% \textbf{Prof. Sophie Sakka}\hfill Professor of Human robot Interaction at Centrale Nantes\\
% Sophie.Sakka@ls2n.fr \hfill +33 (0)2 40 37 69 45\\


\end{document}

%==== References ====%
\header{\textbf{TECHNICAL SUMMARY}}
\vspace{3mm}

